---
title: ""
format: 
  html:
    toc: true
---

# Hands-On Methods for Text-as-Data Research

# Rules of the Workshop

The workshop is intentionally applied. This means that on your laptop, you should download and launch the script. Then:

* Follow the instructor by executing the code and modifying it as needed.

* Complete the exercises.

* Ask questions.

The script is extensively commented, so you can return to any part of it later.

::: {.text-center}
[Download script](https://artur-baranov.github.io/text-as-data/index.qmd){.btn .btn-primary .btn role="button" download="workshop_qta.qmd" style="width:200px" target="_blank"}
:::

In case you do not have RStudio installed, see the instruction [here](https://artur-baranov.github.io/install-R). 

# Brief Coding Recap

First, we start with a quick recap of RStudio.

## Code Chunk

To insert a **Code Chunk**, you can use `Ctrl+Alt+I` on Windows and `Cmd+Option+I` on Mac. Run the whole chunk by clicking the green triangle, or one/multiple lines by using `Ctrl + Enter` or `Command + Return` on Mac.

```{r}
print("Code Chunk")
```

## Function and Arguments, Data structures

Most of the **functions** we want to run require an **argument** For example, the function `print()` above takes the argument "Code Chunk".

```{r}
#| eval: false

function(argument)
```

For example, consider an **object**. Try printing it by highlighting the required line and pressing `Ctrl+Enter` or `Cmd+Return` on Mac.

```{r}
#| results: hold

number = 1
number
print(number)

word = "Northwestern"
word
```

## Libraries

Quite frequently, we use additional libraries to extend the capabilities of R. In this workshop we highly relying on `quanteda` and `tidyverse`. Please, if you do not have these libraries, install them now.

Check if you have them installed

```{r}
c("tidyverse", "quanteda") %in% rownames(installed.packages())
```
If you do not, please install them using the chunk below. **Run it only once!**. Instead of `...` insert the package that is missing. 

```{r}
#| eval: false

install.packages("...")
```

Now, load them into the current R session.

```{r}
#| message: false

library(tidyverse)
library(quanteda)
```


# Quanteda Objects

Quanteda is a widely used R package for quantitative text analysis (QTA), developed by fellow political scientists. It stands for quantitative analysis of textual data.

## Corpus

The collections of documents is called corpus. For example, imagine you have two documents.

```{r}
simple_corpus = corpus(c("A corpus is a set of documents.",
                         "This is the second document in the corpus"))

simple_corpus
```

Additionally, you can add document-level variables. For example, an authorship, number of characters, regions, etc etc. Let's add number of characters in each document. What does `$` operator do? 

```{r}
docvars(simple_corpus)$charcount = nchar(simple_corpus)
```

Let's see the result

```{r}
docvars(simple_corpus)
```

In other words, quanteda stores information about the text separately from the text itself. Important for the future manipulations!

## Tokens
 
Each document consists of tokens. When we tokenize a corpus, the text is segmented into tokens (words or sentences) based on word boundaries. In other words, each word in the document is separated into its own token.

```{r}
simple_toks = tokens(simple_corpus,
                     remove_punct = TRUE)

simple_toks
```

## Document-feature matrix

Represents frequencies of features in documents in a matrix, for example, tokens. Let's constructs a document-feature matrix (DFM) from a tokens object. Run the chunk, take a look on the result. What did DFM do to our data?

```{r}
simple_dfm = dfm(simple_toks)

simple_dfm
```

This allows us to, say, calculate the most frequent words in the whole corpus.

```{r}
topfeatures(simple_dfm, 10)
```


# Bag-of-Words approach

We completely destroy the order of words in our corpus. 


ChatGPT outperforms crowd workers for text-annotation tasks paper



# Check List

- [ ] R doesn't scare me anymore

